Blocks of extended ancestry around selected loci in hybrid zones

### 2016-02-28 drafts/hybrid_zone.tex
a few more edits

We model selection through only a single, underdominant locus:
at this locus, there are two alleles, one corresponding to each of the ancestral populations,
and individuals who are heterozygous at this locus produce on average $1-s$ times as many offspring than either homozygote.
Although most selection in hybrid zones is likely more complex than this simple situation, 
previous work has shown that such models generate clines that are effectively indistinguishable from more complex models of ecological selection \citep{Barton1989, Barton1993},
or complex epistatic systems \plr{CITE}.

@@

@@

Through our simulations we find also that blocks of ancestry that are have crossed the hybrid zone and are closely linked to the selected site without overlapping it (i.e., blocks that are adjacent to the block containing the selected site) are exceptionally short. This is measured by the length of the block adjacent to the block containing the selected site. 
A simple and intuitive explanation for this patter in that loci physically linked to a selected site can only survive on the wrong side of the hybrid zone if they recombine off the background of the unfit variant. 
A disproportionate majority of the subsequent recombination events it experiences will be with the more fit ancestry, and so the ancestry block will decay rapidly. 
This finding suggests that, despite the fact that  haplotypes surrounding incompatibilities might be quite long, genome scans may have the power to extract fine-grained regions near selected loci from the large chunks of ancestry that will often flank these regions.

Our results suggest that a few natural statistical summaries could help identify selected loci in hybrid zones. 
Specifically, the statistic $l_z(k)$ -- the genetic length of ancestry surrounding a site of a given lineage -- and similarly,  and similarly $l_z(k\pm)$, could provide a simple and informative summary. 
This statistic, perhaps in relation to the length of ancestry around adjacent sites, could be developed into an approach to scan genomes from hybrid zones to identify putatively selected loci.

>>>>

We model selection through only a single, underdominant locus:
at this locus, there are two alleles, one corresponding to each of the ancestral populations,
and individuals who are heterozygous at this locus produce on average $1-s$ times as many offspring than either homozygote.
Although most selection in hybrid zones is likely more complex than this simple situation, 
previous work has shown that such models generate clines that are effectively indistinguishable from models of ecological selection or epistatic systems \cite{Kruuk1999,Barton2000a}.

@@

\alisa{For very strong $s$, very few haplotypes are found on the ``wrong" side, and so the signal of longer haplotypes around selected loci may only be present at geographic locations close to the center of the zone. The overall length of the haplotypes decreases as the hybrid zone ages, but the signal remains strong relative to the rest of the genome and detectability will largely depend on the density of ancestry-informative markers.}

@@

Through our simulations we find also that blocks of ancestry that are have crossed the hybrid zone and are closely linked to the selected site without overlapping it (i.e., blocks that are adjacent to the block containing the selected site) are exceptionally short. This is measured by the mean length of the blocks adjacent to the block containing the selected site. A simple and intuitive explanation for this pattern is that loci physically linked to a selected site have recently come from the center of the zone or beyond. Compared to other chromosomes in their new geographic location, these migrants will have on average longer $B$ haplotypes at the selected locus, and shorter $A$ haplotypes nearby. 
This finding suggests that, despite the fact that  haplotypes surrounding incompatibilities might be quite long, genome scans may have the power to extract fine-grained regions near selected loci from the large chunks of ancestry that will often flank these regions.

Our results suggest that a few natural statistical summaries could help identify selected loci in hybrid zones. 
Specifically, the statistic $l_z(k)$ -- the genetic length of ancestry surrounding a site of a given lineage -- and similarly,  and similarly $C(k)$, could provide a simple and informative summary. 
This statistic, perhaps in relation to the length of ancestry around adjacent sites, could be developed into an approach to scan genomes from hybrid zones to identify putatively selected loci.
